What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-01-30 text/01_CogSci_abstract/paper.tex

@@

@@

Posterior predictive checks indicate that the trained model captures patterns of answers at the
aggregate population level well. To have a more fine-grained measure of model fit, we also
looked at posterior predictive $p$-values at the level of subjects and items. Unfortunately,
only the slider rating task, provides enough data for such a fine-grained analysis. For the
slider rating task, fixing a subject and an item, observations and replicates are probability
vectors of length 15. In a first analysis, we used the mean of these probability vectors as a
test statistic. The minimum posterior predictive $p$-value over all 20 (subjects) times 8
(items) cases was 0.13, suggesting that the means of observed $s_{ij}$ are non-surprising to
the trained model. In a second analysis, we used entropy as a test statistic. Two cases gave
posterior predictive $p$-values lower than 0.05. These were from the two participants who gave a
very extreme slider rating for the ``marbles'' item, basically assigning all ``mass'' to the
last bin. What this suggests is that the model can cope reasonably well also with
individual-level data, but has problems accounting for ``extreme'' choices, given that the
population-level hyper-prior on $P_{ij}$ will lead to shrinkage.

>>>>

\ndg{wow, this is weird! you tried softmax ratio of bin probs?}

@@

\ndg{it'd be nice to see some posteriors for some of the (more meaningful) parameters. eg w, kappa, ...}

\ndg{what about the success of the other DMs? looks like give-n is not so hot. worth saying that if so.}

@@

Posterior predictive checks indicate that the trained model captures patterns of answers at the
aggregate population level well. To have a more fine-grained measure of model fit, we also
looked at posterior predictive $p$-values at the level of subjects and items. \ndg{need to say what this means -- i'm not even sure that i know!} Unfortunately,
only the slider rating task, provides enough data for such a fine-grained analysis. For the
slider rating task, fixing a subject and an item, observations and replicates are probability
vectors of length 15. In a first analysis, we used the mean of these probability vectors as a
test statistic. The minimum posterior predictive $p$-value over all 20 (subjects) times 8
(items) cases was 0.13, suggesting that the means of observed $s_{ij}$ are non-surprising to
the trained model. In a second analysis, we used entropy as a test statistic. Two cases gave
posterior predictive $p$-values lower than 0.05. These were from the two participants who gave a
very extreme slider rating for the ``marbles'' item, basically assigning all ``mass'' to the
last bin. What this suggests is that the model can cope reasonably well also with
individual-level data, but has problems accounting for ``extreme'' choices, given that the
population-level hyper-prior on $P_{ij}$ will lead to shrinkage.
\ndg{can say that one possibility (future work) would be to switch to a fatter-tailed distribution relating Q to P, in order to deal with outliers.}
